Arrows for Parallel Computations

### 2017-07-08 paper/content/benchmarks.tex
minor

\performanceSkelRMSM{11213}{32}

\speedupSkelRMSM{11213}{32}

@@

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Parallel performance \\ difference of SkelRM #1 #2}{(Eden - PArrows)}{512}{#3}{
\addplot+[mark=*,thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}
}

@@

\newcommand{\speedupSkelRMDistDiff}[4]{
\speedupdiffplot{Parallel speedup \\ difference of SkelRM #1 #2}{(Eden - PArrows)}{512}{#3}{
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}
}

>>>>

%\performanceSkelRMSM{11213}{32}

%\speedupSkelRMSM{11213}{32}

@@

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Parallel performance difference \\ of SkelRM #1 #2}{(Eden - PArrows)}{512}{#3}{
\addplot+[mark=*,thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}
}

@@

\newcommand{\speedupSkelRMDistDiff}[4]{
\speedupdiffplot{Parallel speedup difference \\ of SkelRM #1 #2}{(Eden - PArrows)}{512}{#3}{
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}
}
